Hypertension and microbiome

### 2019-09-02 articletwo.Rmd
Run error

```{r maaslin means}
pseq.genus.core.table <- pseq.genus.core %>%
    prune_taxa(c("g_Adlercreutzia", "g_Anaerotruncus", "g_Sutterella"), .) %>%
    transform(transform = "compositional") %>%
    psmelt %>%
    mutate(map_groups = relevel(factor(dplyr::ntile(MAP, 3)), ref='1'),
           systm_groups = relevel(factor(dplyr::ntile(SYSTM, 3)), ref='1'),
           Abundance = myscale(Abundance))

>>>>

```{r maaslin means, eval = FALSE}
pseq.genus.core.table <- pseq.genus.core %>%
    prune_taxa(c("g_Adlercreutzia", "g_Anaerotruncus", "g_Sutterella"), .) %>%
    transform(transform = "compositional") %>%
    psmelt %>%
    mutate(map_groups = relevel(factor(dplyr::ntile(MAP, 3)), ref='1'),
           systm_groups = relevel(factor(dplyr::ntile(SYSTM, 3)), ref='1'),
           Abundance = myscale(Abundance))
